Everthing you wanted to know about PanDA but were truly truly afraid to ask

### 2016-12-30 bckground.tex
Preliminary description of Figure 2

>>>>

\subsubsection{High-level Description}

\paragraph{Figure~\ref{fig:atlas_workflow} (1)} Multiple end-users (i.e.,
physicists) submit descriptions of ATLAS Monte Carlo Workflows to the JEDI
component of ATLAS middleware. JEDI supervises the execution of these workflows
through a set of eight predefined stages. Each stage requires a specific type of
input and returns a specific type of output. In this paper, we focus on the
third stage called ``Detector Simulator'': the only one, at the moment, executed
on the HPC resources of Titan.

\paragraph{Figure~\ref{fig:atlas_workflow} (2)} JEDI submits/hands over events
to a PANDA Server. This server manages the execution of all the ATLAS workflows
and their stages, including the ATLAS Monte Carlo Workflow. In
Figure~\ref{fig:atlas_workflow} we depicted only how the events of the third
stage are organized within PANDA Server. Tasks are container of jobs and each
job contains itself a set of events. All the events of each job belongs to a
specific submission of a workflow description and, therefore, to a specific user
(i.e., virtual organization). Tasks should therefore be regarded as multitenant
while jobs and their events as monotenant\mtnote{confirmed?}.

\paragraph{Figure~\ref{fig:atlas_workflow} (3)} Sets of events belonging to
multiple tasks and jobs are pushed/pulled? from the PANDA Server to/by one or
more PANDA Pilot. Sixteen? PANDA Pilots are currently instantiated on a
dedicated DSL node of Titan. These instances are responsible for the packaging
of a set of events into a PBS job script. Packaging is performed on the base of
the information gathered about the availability of backfill resources. Depending
on the amount of nodes available, a specific number of events is packaged into
the PBS script.\mtnote{can the events packaged into a PBS job belong to
different submissions and therefore users?}

\paragraph{Figure~\ref{fig:atlas_workflow} (4)} AthenaMP is used to perform the
simulation of the events within the ATLAS detector, 1 AthenaMP thread for each
core available on the Titan nodes. Currently, 16 threads are used for each node,
each thread being able to simulate an average of 1 event every n??
minutes?/second?. So far, no description has been given of the flow of data
required to simulate each event.
